A weakly structured stem for human origins in Africa

### 2023-02-27 paper.tex
tweak to previous suggestion

We used a subset of populations from the merged  sequencing data from the
African Diversity Reference Panel (ADRP) \citep{Gurdasani2015-qy,Pagani2015-pz}
and the Thousand Genomes Project (1KGP)
\citep{1000_Genomes_Project_Consortium2015-zq} \sgcomment{This sounds like the Nama are from the 2015 paper. Perhaps: 
We generated a sequencing dataset by combining existing and new populations recruited as part of the 
African Diversity Reference Panel (ADRP) \citep{Gurdasani2015-qy,Pagani2015-pz},
as well as Thousand Genomes Project populations (1KGP)
\citep{1000_Genomes_Project_Consortium2015-zq} 
}. These included the Amhara,
Bakiga, Gumuz, Nama, Oromo, Somali, and Zulu from ADRP, and ESN, GWD, LWK, MSL,
YRI, CEU, GBR, CHB, and PJL from 1KGP. After filtering for relatedness and
retaining Nama individuals with $>70\%$ estimated Khoe-San ancestry, we focused on
data from 289 individuals, including 44 Nama individuals. These were merged
with the high-coverage Neanderthal genome from Vindija Cave
\citep{Prufer2017-kk}. We kept variants from regions that fell within the 1KGP
srict callability mask, overlapped with at least 100 continuously called base
pairs in the Neanderthal genome, and were annotated as intergenic.
\texttt{ADMIXTURE} and PCA analyses were conducted on a subset of variants
filtered to remove variants in high LD ($r^2$ threshold of $0.1$). See SI
section \ref{sec:data-sequencing} for additional details on data and
sequencing.

>>>>

We used a subset of populations from the merged  sequencing data from the
African Diversity Reference Panel (ADRP) \citep{Gurdasani2015-qy,Pagani2015-pz}
and the Thousand Genomes Project (1KGP)
\citep{1000_Genomes_Project_Consortium2015-zq} \sgcomment{This sounds like the Nama are from the 2015 paper. Perhaps: 
We generated a sequencing dataset by combining existing and newly recruited populations who are now part of the 
African Diversity Reference Panel (ADRP) \citep{Gurdasani2015-qy,Pagani2015-pz},
as well as Thousand Genomes Project populations (1KGP)
\citep{1000_Genomes_Project_Consortium2015-zq} 
}. These included the Amhara,
Bakiga, Gumuz, Nama, Oromo, Somali, and Zulu from ADRP, and ESN, GWD, LWK, MSL,
YRI, CEU, GBR, CHB, and PJL from 1KGP. After filtering for relatedness and
retaining Nama individuals with $>70\%$ estimated Khoe-San ancestry, we focused on
data from 289 individuals, including 44 Nama individuals. These were merged
with the high-coverage Neanderthal genome from Vindija Cave
\citep{Prufer2017-kk}. We kept variants from regions that fell within the 1KGP
srict callability mask, overlapped with at least 100 continuously called base
pairs in the Neanderthal genome, and were annotated as intergenic.
\texttt{ADMIXTURE} and PCA analyses were conducted on a subset of variants
filtered to remove variants in high LD ($r^2$ threshold of $0.1$). See SI
section \ref{sec:data-sequencing} for additional details on data and
sequencing.
